Arrangement for DroneGo

### 2020-03-09 PAPER.tex
Updates from Overleaf

Where F is the factor variable, A is the factor load matrix, $a_{ij}$ is the factor load; $\epsilon$ is the special factor

@@

\begin{equation}
    \label{lnct}
\end{equation}

@@

\begin{figure}[htbp]\label{5.2}
	\centering
	\includegraphics[width=.6\textwidth]{5.2.png}
	\caption{ flow diagram of solution}\label{5.2}
\end{figure}

@@

%6.1
\subsection{The risk of loss of culture}

%6.2
\subsection{Concrete Policies}

@@

@@

%7.1
\subsection{}

%7.2
\subsection{}

%7.3
\subsection{}

%7.4
\subsection{}

>>>>

Where F is the factor variable, A is the factor load matrix, $a_{ij}$ is the factor load; $\epsilon$ is the special factor.

@@

\begin{equation}
    \ln C(t)=-8.217+5.59\times 10^{-4}e^{8.70\times 10^{-3}t}\label{lnct}
\end{equation}

@@

\begin{figure}[htbp]\label{5.2}
	\centering
	\includegraphics[width=1\textwidth]{5.2.png}
	\caption{ flow diagram of solution}\label{5.2}
\end{figure}

@@

%6.1
\subsection{The risk of loss of culture}
Statistics show that there are 27 world heritage sites scattered among the 37 risk island countries.These world heritage sites are divided into Cultural site and Natural site.From figure \ref{culture site}, we can see that about 70\% are cultural sites, about 22\% are natural cultural heritage, and another 7\% are in extreme danger.They are of high cultural value.(see appendix for details of world heritage).

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture site.png}
	\caption{ flow diagram of solution}\label{culture site}
\end{figure}

There is an urgent need to protect the vast number of world cultural heritage sites that are scattered among these at-risk island countries.A series of protection policies is very necessary.

%6.2
\subsection{Concrete Policies}
Our team has divided cultural protection into three levels , as shown in figure \ref{culture 3 levels},and proposed corresponding policies.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{culture 3 levels.png}
	\caption{ flow diagram of solution}\label{culture 3 levels}
\end{figure}

@@

(1)\textbf{Establish multimedia language corpus.} Records the unique languages, dialects, and spoken words of island countries, processed into a language resource database. The protection of local languages should begin before large numbers of EDPs leave the country. The support of linguists and local governments is also needed, as are the policy and financial supports of the international community.

(2)\textbf{Set up island language learning institutions.} Establish some island language learning institutions in selected recipient countries. This policy can stimulate the interest of the host country's people in the language and culture of EDPs. It helps to protect the language and culture of EDPs, and at the same time, reduces the conflict between the two peoples, making it easier for EDPs to integrate into the host country.

(3)\textbf{Select coastal countries as host countries.} The EDPs come from almost the tropical island countries that are surrounded by the sea. The choice of littoral states as host country is conducive to the rapid adaptation of EDPs to life after migration and the continuation of the culture of these island countries.

@@

%7.1
\subsection{Liveable Country Index (LCI)}
We selected population density, per capita GDP, per capita freshwater resources, and per capita arable land as indicators to measure the country's settable index. The higher the emigration index, the more able countries are to receive EDPs.

Then we calculated the Liveable Country Index of each country(not include island countries) through the factor analysis method in the SPSS software based on the collected data and selected the country with the LCI greater than 0 as the country suitable for accepting EDPs. The result is shown in figure \ref{Countries_with_eligible_immigration_indices}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{Countries with eligible immigration indices.png}
	\caption{ flow diagram of solution}\label{Countries_with_eligible_immigration_indices}
\end{figure}

%7.2
\subsection{National Responsibility Index (NRI)}
First, we select per capita CO2 emissions and per capita energy consumption as indicators of the National Responsibility Index, because the greenhouse effect is the leading cause of sea-level rise. The higher the National Responsibility Index, the more responsible a country is to accept EDPs.

After that, we normalize per capita CO2 emissionss and per capita energy consumption of countries with LCI value greater than 0, and measure their contribution to the National Responsibility Index with a weighting of 50\% each. The corresponding NRI of 57 countries was obtained. The results are shown in figure \ref{NRI}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{NRI.png}
	\caption{ flow diagram of solution}\label{NRI}
\end{figure}

%7.3
\subsection{International Responsibility Index (IRI)}

When policymakers consider which countries should accept displaced refugees, they should not only consider whether the country has a pleasant living environment or how much it contributes to global warming. They should combine the two to get more objective results. Therefore, we merged LCI and NRI into the International Responsibility Index. Countries with high IRI should give priority to accept EDPs.

The migration index of selected countries was normalized, and the contribution to IRI was measured by weighting LCI and national NRI at 50\% each.

\begin{equation}\label{IRI}
    IRI=0.5\times normalized\,\,LCI+0.5\times NRI
\end{equation}

Through equation \eqref{IRI}, the IRI of 57 countries are shown in figure. \ref{country_index}

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{country_index.png}
	\caption{ flow diagram of solution}\label{country_index}
\end{figure}

We regard countries with an IRI greater than 0.3 to be high. To simplify the subsequent calculations, we used only high-index countries. The result is shown in figure \ref{high_index_countries}.

\begin{figure}[htbp]
	\centering
	\includegraphics[width=.8\textwidth]{high_index_countries.png}
	\caption{ flow diagram of solution}\label{high_index_countries}
\end{figure}

%7.4
\subsection{The influence of geographical distance on resettlement}

%7.5
\subsection{Comprehensive Index}
